Reading Notes

### 2020-09-14 2pd.tex
incorporating edits and final pass

Organic photovoltaics (OPVs, see~\autoref{opv}) are a focus of this research because they represent the best opportunity for cost-effective solar power.
The theoretical efficiency limit (Shockley-Queisser limit) for a p-n single junction solar cell is about 30\%\cite{Shockley1961}.
Multijuction cells may achieve efficiencies that surpass this limit, but they often do not have lower energy payback times as their production is more costly.
\autoref{nrel} shows the efficiency gains made by single junction silicon and organic photovoltaic devices over the last 30 years.
These are merely a selection among the many categories of PV devices.
The trend of the silicon cells shows that the efficiency gain is levelling off as the devices approach the Shockley-Queisser limit.
OPV devices, however, still have a lot of room for improvement, and recent increases in efficiency reflect this.
\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}
    \caption{(a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process. Part (a) adapted from ref~\cite{Dou2013}. Parts (b,c,d) adapted from ref~\cite{Miller2018c}.}\label{opv}
\end{wrapfigure}
Many of the latest advancements in OPV technology have been through specialized processing or combinations of new chemistries.
One new chemical moiety which has recieved attention is the ladder backbone structure seen in many non-fullerene acceptors (NFAs), see \autoref{chemistries}.
In 2018, a single junction cell using an NFA achieved a record-breaking 13.25\% efficiency\cite{raynergy}.
And in 2019, a cell using an NFA functionalized with chlorine groups was found to achieve 16.5\% efficiency\cite{Cui2019}. 
Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70--80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
(but how these molecules interact with donor polymers is not yet known and there's >1000 of them and there have been some metrics devised to figure out how to narrow them down like flory-huggins interaction parameter, but it's still really hard.) \cite{Gao2020} %% transition attempt
Ultimately, the efficiency of a solar cell depends on the self-assembly of its active layer.

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/chem_structures.pdf}
    \caption{Chemical structures of polymer donors (P3HT and PTB7) and acceptors --- fullerene (PC$_{61}$BM) and non-fullerene (ITIC).}\label{chemistries}
\end{wrapfigure}
\noindent With minor modifications, the number of compounds and the processing conditions can become an intractable problem for experiment (see~\autoref{chemistries}).
The number of possibilities compounds provides an opportunity for better OPVs, but it also increases the scope of the problem.
Imagine, you are a chemist preparing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, ITIC, and a polymer donor, PTB7. 
Each compound costs \$500 for 100 mg\cite{sigmaaldrich}.
The solvent you use and the concentrations of your active compounds changes the device performance\cite{Hoppe2004a}.
The amount of time the solvent is allowed to evaporate changes the device performance\cite{Li2007}.
The time and temperature of the thermal annealing changes the device performance\cite{Ma2005}.
The regioregularity of your polymer affects the device performance\cite{Kim2006}.
The distribution of polymer lengths affects the device performance\cite{Zhao2013b}.
Seemingly minor changes to the functional groups on either species affects the device performance\cite{Swick2019a}.
All these parameter require consideration just to determine the performance of one donor/acceptor combination in one category of potential compounds\cite{Dou2013}.
This is where molecular simulation can help.
By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will form the morphology with the best charge transport, and in turn, help to solve the energy crisis.

Simulating an OPV morphology requires careful consideration. %% reword
A complication of the simulation of OPV polymers is that the properties which predict a device's efficiency, for example charge transport, span multiple length scales.
So, in order to model this system, a multiscale approach is necessary.
By breaking our simulation apart into separate steps and equilibrating different lengths scales individually, we can get equilibrated morphologies on multiple length scales more efficiently.
Another complication of this research is its computational scope.
If this project is going to have the desired impact (i.e., using molecular simulation to identify novel OPVs), every step of the process and the resulting data must be reproducible and validated.
The nature of a multiscale simulation requires translation between formats and units and accurate handling of large data, and thus requires infrastructure to reduce error.
By adhering to recent guidelines in the computational sciences community, we can strive to design tools which are transferrable, reproducibile, usable, and extensible (TRUE)\cite{Thompson2020}.
Although the molecular and computational scope of this project is broad, by using and building upon existing architectures we can manage the multiscale nature of this project and contribute to reproducible science. %% omg help words are hard.

For this research we propose to develop a flexible method for specifying coarse-grained models to obtain OPV polymer morphologies equilibrated on length scales relevant to charge transport.
We also propose to develop a backmapping method, which works on the same simple mapping operator, to restore the atomic positions in preparation for techniques which require atomic level resolution, e.g., charge transport calculations.
This two step process is necessary because starting with the fully atomistic structure would not only be computationally inefficient but also the result may be less accurate due to the difficulties of equilibrating polymers\cite{Gartner2019a}.
This efficiency is important because the scope of potential OPV compounds is vast and the energy crisis necessitates expediency.
The number of OPV compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.
There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors (NFAs) have been recieving attention for their potential to achieve higher efficiencies than their fullerene counterparts\cite{Dou2013}.
Coarse grain models do not yet exist for many of these NFAs, and with so many varieties an adaptable pipeline makes more sense than a single model.
It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies.

@@

Ultimately the goal this research is to help solve the global energy crisis. 
Solar energy is an important part of a green energy solution.
This research aims to gain insight about new OPV compound morphologies using molecular simulation.
In order to achieve this goal, we have defined the following objectives:
\begin{enumerate}
    \item {Develop a generalized toolset for coarse-graining and performing simulations of novel molecules for organic photovoltaics}
    \item {Develop a general tool to calculate atomistic positions from a coarse-grained morphology}
    \item {Predict nanostructures of novel OPV chemistries}
    \item {Identify chemical features correlated with robust self-assembly}
    \item {Identify chemical features correlated with good charge transport}
\end{enumerate}

In order to model these OPV polymer systems on relevant length scales, it is necessary to develop new coarse-grained models.
A flexible and efficient coarse-graining scheme will simplify the process of mapping and parameterizing these coarse-grained elements.

The flexibility of specifying a mapping will allow for the comparison of multiple mappings which may provide insight into the features of an OPV which govern its self-assembly and the limits of coarse-grained models.
Currently there is no agreed-upon ``best'' scheme for a coarse-grained mapping operator.
By making a simple and easy-to-use coarse-graining tool, many mapping operators can be tested and the limits of a minimal model can be probed.

@@

The first OPV was created by Tang in 1986 and used a bilayer structure containing copper phthalocyanine and a perylene derivitive\cite{Tang1986b}. 
This early device had a PCE of 0.95\%.
In 1992, Sariciftci and Heeger were the first to report using a fullerene as an electron acceptor in a fullerene:polymer mixture\cite{Sariciftci1992}.
And in 1995, Yu described the first bulk heterojunction (BHJ), as an interpenetrating network of donor and acceptor that maximizes the interfacial area, which is still the state of the art morphology to this day\cite{Yu1995}.
Most recently, non-fullerene acceptors (NFAs), like ITIC, are contributing to the PCE increase of modern OPVs\cite{S.Gurney2019b}.

@@

The compounds which compose an OPV are synthesizable molecules (often polymers) composed of abundant elements (carbon, hydrogen, nitrogen, sulfur, oxygen).
Due to the conjugated pi-orbitals in these molecules the absorption of sunlight can excite an electron into a frontier orbital and generate an exciton, a couloubicly bound electron-hole pair.
OPVs are made as a mixture of electron-donor and electron-acceptor compounds in a structure called a bulk heterojunction.
Depending on the bulk morphology of these compounds, the exciton can travel to an acceptor-donor interface and dissociate into free electron and hole then these free charges generate current if they can subsequently make their way to an electrode.

@@

%% transition???
The first MD simulation modelled a system of 108 particles and completed 200 collisions in one hour on an IBM-704\cite{Alder1957}.
Now GPUs are a 100 million times faster.
Due to its the simplicity and efficient scaling, MD is now commonly used for the modelling of protein folding\cite{levitt75} and other biological processes, and investigating the bulk properties of polymers\cite{Gartner2019a}.

@@

Even with the simplifications of MD, we are still not able to simulate many systems efficiently on relevant length scales.
By abstracting away some of the atomic degrees of freedom which do not contribute as much to the bulk structure, MD can be used to look at even larger systems.
Coarse grain models are one such technique to increase the length and time scales examined by a simulation.

\subsection*{Coarse Grain Models}

Coarse graining refers to grouping atoms in a structure into a ``super atom'' and using an effective potential to represent the resulting coarse-grained site.
This effective potential used to represent the reduced system results in a smoothed free energy landscape. 
The heart of coarse-graining is the removal of degrees of freedom. 
Coarse grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models by abstracting away irrelevant degrees of freedom.
Processes which may have taken many time steps in an all atom simulation can take fewer time steps in a coarse simulation\cite{Berendsen2010}.
Due to their long length and time scales, coarse-grained models are ideal for examining polymer properties\cite{Gartner2019a}.
Similarly to how monitoring the working of a plant cell is not necessary to understanding the growth of a forest, some atomic level properties do not need consideration when simulating the bulk morphology\cite{Muller-Plathe2002}.
It is too big, too slow, and unwise to simulate huge boxes of atomistic polymers.
Even if the simulation was to complete, there would be too much information to process accurately. 
Coarse graining allows scientists to \textit{focus} their experiments\cite{Baschnagel2000}.

The resolution of coarse-grained systems is broad:
Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible\cite{Paul1995a, Yang2006a}.
Other coarse-graining schemes may group functional groups together\cite{Berendsen2010, Jankowski2013, Marsh2014}, one site per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019}.
General coarse-grained models of OPV thiophene polymers where only the spacing and regioregularity of the side chains were varied were able to predict order disorder transitions and scattering patterns comparable to those obtained from experiment\cite{Jankowski2013, Marsh2014}.
A coarse-grained model for phospholipids has allowed for bilayer formation from an initial random configuration to be simulated even though the model was parameterized to the vapor-liquid phase transition\cite{Shelley2001}.
Which model is right depends on the length and time scale on which the property of interest can be observed.

For many systems, however, we are interested in properties which span length scales.
For instance, in a system like a OPV polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5--10 nm)\cite{Huang2010}; it is the wrong tool for the job.
If what we are interested in is the properties of the polymer in the bulk heterojunction, then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure.
Once a good bulk structure has been achieved, the atomistic details can be reintegrated much more easily: a process called backmapping.
In the same way that a coarse-grained model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simulation from a coarse-grained structure.
The large length scale, polymer level properties can be equilibrated during the coarse-grained simulation, and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores \textit{and} the connectivity of these chromophores over distances proportional to the exciton dissociation length.

%% HELP transition?
%%<what stands in our way?>
%%<coarse-grain models are specific>
%% EJ: Discuss in-person?
%% HELP is the following paragraph/section too big? 
%% EJ: It's a little rambly, but definitely not bad. One check we can do in the background is check for each paragraph or subsection, have we clearly identified outstanding problems or gaps in knowledge, and check whether mention them in the motivation? I expect this kind of check will help "tidy up" this paragraph.
Part of coarse-graining process that is not yet automated is choosing a mapping scheme or a mapping operator.
A mapping operator defines which atoms are grouped into a ``super atom'' represented by one coarse-grained site and where the site is placed relative to the atom group.
Mapping operators are chosen based on the desired resolution of the coarse-grained system and the information to be extracted.
A straightforward way to define a mapping operator is to group a set number of heavy atoms (non hydrogen) together; this is the method used in the notable MARTINI force field\cite{Marrink2007}.
In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
When parameterizing a new molecule for the MARTINI method, a user must pick a mapping and then compare the chemical structure of the resulting sites to those which have already been parameterized; a process which is time consuming and error prone\cite{martini-tutorial}.
The published tutorial recommends searching through existing MARTINI topologies to find similar structures and then manually editing them to fit the new molecule.
Whether the structure is similar then is based on the user's chemical knowledge, judgement, and intuition.
Many other mapping schemes also rely on the user's chemical intuition (e.g., grouping the atoms in ring structures which move less or grouping structures based on the dominant interactions, like the base pairs in DNA)\cite{Huang2010, Knotts2007}.
As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically and manually deciding a mapping operator becomes more difficult.

There have been efforts to create algorithms for automating the process of deciding which atoms are grouped in a ``super atom''.
One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the ``best'' mapping by comparing the difference between the mapped RDF and velocity autocorrelation function\cite{Chakraborty2018b}.
Another uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the ``expert'' mapping chosen using chemical intuition reliably\cite{Li2020}. 
A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.
However, there is still no best method for choosing the mapping operator.
Deciding on a mapping operator is just the first step of creating a coarse-grained model, next is to create an effective potential for the site.

@@

There are numerous methods for deriving coarse-grained potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
IBI is where a coarse-grained potential is iteratively tuned to fit a target distribution usually from an atomistic simulation\cite{Reith2003}.
The radial distribution function (RDF) describes the probability of finding a particle at a given distance from another particle.
The RDF can be used to investigate properties such as the density or the phase of a system and the RDF is used in IBI as the target distribution for the non-bonded potentials. %%reword?
The process for determining the non-bonded potentials using IBI is as follows:
\begin{enumerate}
    \item 
        The coarse-grained system is mapped onto an equilibrated atomistic one.

@@

        Where $F(r)$ is the PMF, $k_{B}T$ is the thermal energy, and $g(r)$ is the target distribution.
        Although $F(r)$ is a free-energy and not a potential energy, it is sufficient to be used as the initial potential ($V_{0}$) in the iterative scheme\cite{Reith2003}.

    \item
        A simulation can be run using the PMF as the non-bonded potential to achieve a new distribution.

    \item
        The difference between the new and target distribution can be accounted for in the next iteration accoring to the following equation:

@@

The coarse-grained potential derived from IBI is not transferrable to different thermodynamic statepoints.
This is because the RDF is a property of the ensemble average at a given statepoint, so the potential derived from this property is also limited.
For example, separate potentials are required to capture solid and fluid structures of a pure simple lipid~\cite{Hadley2010a}.
There are many attempts to create transferrable CG potentials, for example:
The TraPPE force-field fits CG potentials using vapor-liquid equilibria to improve transferrability across thermodynamic states\cite{Maerzke2011}.
But optimization to the liquid-vapor equilibrium, although useful for prediction of thermodynamic properties, may not be ideal for prediction of structure which will strongly influence charge transport.

@@

Multistate iterative Boltzmann inversion (MS IBI) includes data from multiple targets to yield a less state dependent potential\cite{Moore2014}.
The MS IBI potential is an average of the single state potentials with a weighting function to prioritize a state of interest, as shown in the following equation:
\[
    V_{s,i+1}(r) = V_{s,i}(r) - \frac{1}{N}\sum_{s}\alpha_{s}(r)k_{B}T_{s} \ln\bigg(\frac{g_{s}^{i}(r)}{g_{s}(r)}\bigg)
\]
where the subscript $s$ represents the property at that state, $N$ is the total number of states, and $\alpha_{s}(r)$ is a weighting factor allowing for more or less emphasis on each state.
This method has been shown to accurately reproduce the true potential in monoatomic LJ fluid\cite{Moore2014}.
When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
If this overlap region is large, there are many potentials which will provide matching RDFs (see \autoref{moore}).
For some systems there may not be a potential that represents all states.

%% HELP transition
%%<need some tie in back to why we would want to go from CG--->atomistic>
%% EJ: Chat in-person

@@

%%\begin{wrapfigure}{L}{0.5\linewidth}
%%    \centering
%%    \includegraphics[width=\linewidth]{images/hexanexml.pdf}
%%    \caption{XML file used by VOTCA to specify a three site coarse-grained mapping of n-hexane}
%%    \label{hexanexml}
%%\end{wrapfigure}

>>>>

Organic photovoltaics (OPVs, see~\autoref{opv}) are a focus of this research because they represent the best opportunity for cost-effective solar power.
The theoretical efficiency limit (Shockley-Queisser limit) for a p-n single junction solar cell is about 30\%\cite{Shockley1961}.
Multijuction cells may achieve efficiencies that surpass this limit, but they often do not have lower energy payback times as their production is more costly.
\autoref{nrel} shows the efficiency gains made by single junction silicon and organic photovoltaic devices over the last 30 years.
These are merely a selection among the many categories of PV devices.
The trend of the silicon cells shows that the efficiency gain is levelling off as the devices approach the Shockley-Queisser limit.
OPV devices, however, still have a lot of room for improvement, and recent increases in efficiency reflect this.
\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}
    \caption{(a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process. Part (a) adapted from ref~\cite{Dou2013}. Parts (b,c,d) adapted from ref~\cite{Miller2018c}.}\label{opv}
\end{wrapfigure}
Many of the latest advancements in OPV technology have been through specialized processing or combinations of new chemistries.
One new chemical moiety which has recieved attention is the ladder backbone structure seen in many non-fullerene acceptors (NFAs), see \autoref{chemistries}.
In 2018, a single junction cell using an NFA achieved a record-breaking 13.25\% efficiency\cite{raynergy}.
And in 2019, a cell using an NFA functionalized with chlorine groups was found to achieve 16.5\% efficiency\cite{Cui2019}. 
Not only are NFAs found to be more efficient, but they also show to be more stabile in air than polymer:fullerene blends (retaining 70--80\% of the PCE after 1,200 h exposed to air while the fullerene device was no longer operational after 800 h)\cite{Baran2017}.
But how these new chemistries will interact with donor polymers is still an active area of research.
With thousands of variations, attempts to predict which combinations of chemistries will result in the best structure are vital to narrowing the search\cite{Gao2020} as ultimately the efficiency of a solar cell depends on the self-assembly of its active layer.

@@

\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/chem_structures.pdf}
    \caption{Chemical structures of polymer donors (P3HT and PTB7) and acceptors --- fullerene (PC$_{61}$BM) and non-fullerene (ITIC).}\label{chemistries}
\end{wrapfigure}
\noindent With minor modifications, the number of compounds and the processing conditions can become an intractable problem for experiment (see~\autoref{chemistries}).
The number of possible compounds provides an opportunity for better OPVs, but it also increases the scope of the problem.
Imagine, you are a chemist preparing and testing new OPV morphologies: you are specifically looking at a mixture of a non-fullerene acceptor, ITIC, and a polymer donor, PTB7. 
Each compound costs \$500 for 100 mg\cite{sigmaaldrich}.
The solvent you use and the concentrations of your active compounds changes the device performance\cite{Hoppe2004a}.
The amount of time the solvent is allowed to evaporate changes the device performance\cite{Li2007}.
The time and temperature of the thermal annealing changes the device performance\cite{Ma2005}.
The regioregularity of your polymer affects the device performance\cite{Kim2006}.
The distribution of polymer lengths affects the device performance\cite{Zhao2013b}.
Seemingly minor changes to the functional groups on either species affects the device performance\cite{Swick2019a}.
All these parameters require consideration just to determine the performance of one donor/acceptor combination in one category of potential compounds\cite{Dou2013}.
This is where molecular simulation can help.
By using a simulation pipeline, we can help to streamline the process of determining which OPV materials will robustly self-assemble into the morphology with the best charge transport, and in turn, help to solve the energy crisis.

Simulating an OPV morphology, however, requires careful consideration. %% reword
A complication of the simulation of OPV polymers is that the properties which predict a device's efficiency, for example charge transport, span multiple length scales.
So, in order to model this system, a multiscale approach is necessary.
By breaking our simulation apart into separate steps and equilibrating different length scales individually, we can get equilibrated morphologies more efficiently.
Another complication of this research is its computational scope.
If this project is going to have the desired impact (i.e., using molecular simulation to identify novel OPVs), every step of the process and the resulting data must be reproducible and validated.
The nature of a multiscale simulation requires translation between formats and units and accurate handling of large data, and thus requires infrastructure to reduce error.
By adhering to recent guidelines in the computational sciences community, we can strive to design tools which are transferrable, reproducibile, usable, and extensible (TRUE)\cite{Thompson2020}.
Although the molecular and computational scope of this project is broad, by using and building upon existing architectures we can manage the multiscale nature of this project and contribute to reproducible science. %% omg help words are hard.

For this research we propose to develop a flexible method for specifying coarse grain (CG) models to obtain OPV polymer morphologies equilibrated on length scales relevant to charge transport.
We also propose to develop a backmapping method, which works on the same mapping operator, to restore the atomic positions in preparation for techniques which require atomic level resolution, e.g., charge transport calculations.
This two step process is necessary because starting with the fully atomistic structure would not only be computationally inefficient, but also the result may be less accurate due to the difficulties of equilibrating polymers\cite{Gartner2019a}.
This efficiency is important because the scope of potential OPV compounds is vast and the energy crisis necessitates expediency.
The number of OPV compounds to test quickly becomes intractable when we consider that the power conversion efficiency is strongly linked to minor chemical modifications or functionalization, device processing, and the interplay between donor and acceptor\cite{Mazzio2015,Swick2019a}.
There are countless variations of electron donor polymers, fullerene acceptors, and more recently small molecule, non-fullerene acceptors have been recieving attention for their potential to achieve higher efficiencies than their fullerene counterparts\cite{Dou2013}.
Coarse-grain models do not yet exist for many of these NFAs, and with so many varieties an adaptable pipeline makes more sense than a single model.
It is necessary to develop a simple, useable, and flexible pipeline to adapt to the constantly changing chemistries of current OPV technologies.

@@

Ultimately the goal this research is to help solve the global energy crisis. 
Solar energy is an important part of a green energy solution.
This research aims to gain insight about new OPV compound morphologies using molecular simulation.
In order to achieve this goal, we have defined the following objectives:
\begin{enumerate}
    \item {Develop a generalized toolset for creating CG models and performing simulations of novel molecules for organic photovoltaics}
    \item {Develop a general tool to calculate atomistic positions from a CG morphology}
    \item {Predict nanostructures of novel OPV chemistries}
    \item {Identify chemical features correlated with robust self-assembly}
    \item {Identify chemical features correlated with good charge transport}
\end{enumerate}

In order to model these OPV polymer systems on relevant length scales, it is necessary to develop new CG models.
A flexible and efficient CGing scheme will simplify the process of mapping and parameterizing these models.

The flexibility of specifying a mapping will allow for the comparison of multiple mappings which may provide insight into the features of an OPV which govern its self-assembly and the limits of CG models.
Currently there is no agreed-upon ``best'' scheme for a mapping operator.
By making a simple and easy-to-use CGing tool, many mapping operators can be tested and the limits of a minimal model can be probed.

@@

The first OPV was created by Tang in 1986 and used a bilayer structure containing copper phthalocyanine and a perylene derivitive\cite{Tang1986b}. 
This early device had a PCE of 0.95\%.
In 1992, Sariciftci and Heeger were the first to report using a fullerene as an electron acceptor in a fullerene:polymer mixture\cite{Sariciftci1992}.
And in 1995, Yu described the first bulk heterojunction (BHJ), as an interpenetrating network of donor and acceptor that maximizes the interfacial area, which is still the state of the art morphology to this day\cite{Yu1995}.
Most recently, NFAs like ITIC are contributing to the PCE increase of modern OPVs\cite{S.Gurney2019b}.

@@

The compounds which compose an OPV are synthesizable molecules (often polymers) composed of abundant elements.
Due to the conjugated pi-orbitals in these molecules the absorption of sunlight can excite an electron into a frontier orbital and generate an exciton, a couloubically bound electron-hole pair.
OPVs are made as a mixture of electron-donor and electron-acceptor compounds in a structure called a bulk heterojunction.
Depending on the bulk morphology of the compound mixture, the exciton can travel to an acceptor-donor interface and dissociate into free electron and hole.
Then the free charges can generate current if they can subsequently make their way to an electrode.

@@

%% transition???
The first MD simulation modelled a system of 108 particles and completed 200 collisions in one hour on an IBM-704\cite{Alder1957}.
Now GPUs are a 100 million times faster.
Due to its simplicity and efficient scaling, MD is now commonly used for the modelling of protein folding\cite{levitt75} and other biological processes, and investigating the bulk properties of polymers\cite{Gartner2019a}.

@@

Even with the simplifications of MD, we are still not able to simulate many systems efficiently on relevant length scales.
By abstracting away some of the atomic degrees of freedom which do not contribute as much to the bulk structure, MD can be used to look at even larger systems.
Coarse-grain models are one such technique to increase the length and time scales examined by a simulation.

\subsection*{Coarse-Grain Models}

Coarse-graining refers to grouping atoms in a structure into a ``super atom'' and using an effective potential to represent the resulting CG site.
This effective potential used to represent the reduced system results in a smoothed free energy landscape. 
The heart of CGing is the removal of degrees of freedom. 
Coarse-grain models allow for simulators to access length and time scales that would be otherwise impossible using atomistic models by abstracting away irrelevant degrees of freedom.
Processes which may have taken many time steps in an all atom simulation can take fewer time steps in a coarse simulation\cite{Berendsen2010}.
Due to their long length and time scales, CG models are ideal for examining polymer properties\cite{Gartner2019a}.
Similarly to how monitoring the working of a plant cell is not necessary to understanding the growth of a forest, some atomic level properties do not need consideration when simulating the bulk morphology\cite{Muller-Plathe2002}.
It is too big, too slow, and unwise to simulate huge boxes of atomistic polymers.
Even if the simulation was to complete, there would be too much information to process accurately. 
Coarse-graining allows scientists to \textit{focus} their experiments\cite{Baschnagel2000}.

The resolution of CG systems is broad:
Simply grouping hydrogens with the heavy atom they are bonded to, called the united-atom model, has been shown to speed up dynamics and make polymer length scales more easily accesible\cite{Paul1995a, Yang2006a}.
Other CGing schemes may group functional groups together\cite{Berendsen2010, Jankowski2013, Marsh2014}, one site per repeat unit in a polymer\cite{Lee2011}, or even represent an entire amino acid with a single site\cite{Peng2019}.
General CG models of OPV thiophene polymers where only the spacing and regioregularity of the side chains were varied were able to predict order disorder transitions and scattering patterns comparable to those obtained from experiment\cite{Jankowski2013, Marsh2014}.
A CG model for phospholipids has allowed for bilayer formation from an initial random configuration to be simulated even though the model was parameterized to the vapor-liquid phase transition\cite{Shelley2001}.
Which model is right depends on the length and time scale on which the property of interest can be observed.

For many systems, however, we are interested in properties which span length scales.
For instance, in a system like a OPV polymer melt, it is not only computationally intractable to try and simulate the electron density on length scales proportional to the exciton dissociation length (~5--10 nm)\cite{Huang2010}; it is the wrong tool for the job.
If what we are interested in is the properties of the polymer in the bulk heterojunction, then it is wise to abstract away any degrees of freedom which do not directly contribute to the self-assembly of the structure.
Once a good bulk structure has been achieved, the atomistic details can be reintegrated much more easily: a process called backmapping.
In the same way that a CG model can be mapped onto an atomistic one, we can get a reasonable starting structure for an atomistic simulation from a CG structure.
The large length scale, polymer level properties can be equilibrated during the CG simulation, and then the atomic interactions can be equilibrated during the backmapped atomistic simulation.
This can allow us the calculate properties such as charge transport, which depends upon the electronic structure of individual chromophores \textit{and} the connectivity of these chromophores over distances proportional to the exciton dissociation length.

%% HELP transition?
%%<what stands in our way?>
%%<CG models are specific>
%% EJ: Discuss in-person?
%% HELP is the following paragraph/section too big? 
%% EJ: It's a little rambly, but definitely not bad. One check we can do in the background is check for each paragraph or subsection, have we clearly identified outstanding problems or gaps in knowledge, and check whether mention them in the motivation? I expect this kind of check will help "tidy up" this paragraph.
Part of CGing process that is not yet automated is choosing a mapping scheme or a mapping operator.
A mapping operator defines which atoms are grouped into a CG site and where the site is placed relative to the atom group.
Mapping operators are chosen based on the desired resolution of the CG system and the information to be extracted.
A straightforward way to define a mapping operator is to group a set number of heavy (non hydrogen) atoms together; this is the method used in the notable MARTINI force field\cite{Marrink2007}.
In this scheme, four atoms (except rings, which are treated differently) are grouped and the site is classified as polar, non-polar, apolar, or charged depending on the atoms it is composed of.
When parameterizing a new molecule for the MARTINI method, a user must pick a mapping and then compare the chemical structure of the resulting sites to those which have already been parameterized; a process which is time consuming and error prone\cite{martini-tutorial}.
The published tutorial recommends searching through existing MARTINI topologies to find similar structures and then manually editing them to fit the new molecule.
Whether the structure is similar then is based on the user's chemical knowledge, judgement, and intuition.
Many other mapping schemes also rely on the user's chemical intuition (e.g., grouping the atoms in ring structures which move less or grouping structures based on the dominant interactions, like the base pairs in DNA)\cite{Huang2010, Knotts2007}.
As the number of atoms in the fine grain structure increases, the number of possible mappings increase drastically and manually deciding a mapping operator becomes more difficult.

There have been efforts to create algorithms for automating the mapping operator.
One study reduced the number of allowed mappings by only allowing those which do not change the symmetry group, then iterated over a graph of all possible mappings to find the ``best'' mapping by comparing the difference between the mapped RDF and velocity autocorrelation function\cite{Chakraborty2018b}.
Another uses principle component analysis to choose a mapping scheme for biomolecules that best represents th essential dynamics\cite{Zhang2008}.
Mapping operators can be automated using machine learning: clustering methods combined with graph analysis were shown to predict the ``expert'' mapping chosen using chemical intuition reliably\cite{Li2020}. 
A mapping operator based on the centers of charge was shown to accurately model electrostatic properties\cite{Cao2015a}.
However, there is still no best method for choosing the mapping operator.
Deciding on a mapping operator is just the first step of creating a CG model, next is to create an effective potential for the site.

@@

There are numerous methods for deriving CG potentials from atomistic ones (e.g., force-matching, reverse Monte Carlo), but in this proposal we will focus on Iterative Boltzmann Inversion (IBI).
In IBI a CG potential is iteratively tuned to fit a target distribution usually from an atomistic simulation\cite{Reith2003}.
The radial distribution function (RDF) describes the probability of finding a particle at a given distance from another particle.
The RDF can be used to investigate properties such as the density or the phase of a system and the RDF is used in IBI as the target distribution for the non-bonded potentials. %%reword?
The process for determining the non-bonded potentials using IBI is as follows:
\begin{enumerate}
    \item 
        The CG system is mapped onto an equilibrated atomistic trajectory.

@@

        Where $k_{B}T$ is the thermal energy and $g(r)$ is the target distribution.
        Although $F(r)$ is a free-energy and not a potential energy, it is sufficient to be used as the initial potential ($V_{0}$) in the iterative scheme\cite{Reith2003}.

    \item
        A simulation is run using the PMF as the non-bonded potential to achieve a new distribution.

    \item
        The potential is adjusted by the ratio of the new and target distribution in the next iteration accoring to the following equation:

@@

The CG potential derived from IBI is not transferrable to different thermodynamic statepoints.
This is because the RDF is a property of the ensemble average at a given statepoint, so the potential derived from this property is also limited.
For example, it was found that separate potentials are required to capture solid and fluid structures of a pure simple lipid~\cite{Hadley2010a}.
There are many efforts to create transferrable CG potentials, for example:
The TraPPE force-field fits CG potentials using vapor-liquid equilibria to improve transferrability across thermodynamic states\cite{Maerzke2011}.
But optimization to the liquid-vapor equilibrium, although useful for prediction of thermodynamic properties, may not be ideal for prediction of structure which will strongly influence charge transport.

@@

Multistate iterative Boltzmann inversion (MS IBI) includes data from multiple targets to yield a less state dependent potential\cite{Moore2014}.
The MS IBI potential is a weighted average of the single state potentials, as shown in the following equation:
\[
    V_{s,i+1}(r) = V_{s,i}(r) - \frac{1}{N}\sum_{s}\alpha_{s}(r)k_{B}T_{s} \ln\bigg(\frac{g_{s}^{i}(r)}{g_{s}(r)}\bigg)
\]
Where the subscript $s$ represents the property at that state, $N$ is the total number of states, and $\alpha_{s}(r)$ is a weighting function allowing for more or less emphasis on a particular state.
The MS IBI method has been shown to accurately reproduce the true potential in monoatomic LJ fluid\cite{Moore2014}.
And it has been successfully extended to n-dodecane\cite{Moore2014}, biomolecular systems\cite{Moore2016}, and semi-crystalline polyethylene\cite{Agrawal2016}.
When using the MS IBI method, it is important to choose dissimilar states to minimize the potential overlap region.
If this overlap region is large, there are many potentials which will provide matching RDFs (see \autoref{moore}).
For some systems there may not be a potential that represents all states.
With these considerations, the MS IBI method can be automated and fits well into a workflow for parameterizing forcefields for novel OPV chemistries.
The potential obtained using MS IBI can then be used to equilibrate a CG system which is the first step to predicting the efficiency of an OPV morphology.
%% HELP transition
%%<need some tie in back to why we would want to go from CG--->atomistic>
%% EJ: Chat in-person

@@

%%\begin{wrapfigure}{L}{0.5\linewidth}
%%    \centering
%%    \includegraphics[width=\linewidth]{images/hexanexml.pdf}
%%    \caption{XML file used by VOTCA to specify a three site CG mapping of n-hexane}
%%    \label{hexanexml}
%%\end{wrapfigure}
